A Toolbox for Manipulating and Assessing Color Palettes

### 2020-11-09 pkg/colorspace/paper/Toolbox/article.Rmd
document the recent additions: binned ggplot2 color scales, and cvd option in swatchplot
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@570 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

To provide access to the HCL color palettes from within \pkg{ggplot2} graphics [@color:ggplot2; @color:ggplot2pkg]
suitable discrete and/or continuous \pkg{ggplot2} color scales are provided.
The scales are named via the scheme

@@

- `<aesthetic>` is the name of the aesthetic (`fill`, `color`, `colour`).
- `<datatype>` is the type of the variable plotted (`discrete` or `continuous`).
- `<colorscale>` sets the type of the color scale used (`qualitative`, `sequential`, `diverging`, `divergingx`).

@@

The function `swatchplot()` is a convenience function for displaying
collections of palettes that can be specified as lists or matrices of
hex color codes. Essentially, it is just a call to the base graphics
`rect()` function but with heuristics for choosing default labels, margins,
spacings, borders, etc. These heuristics are selected to work well for `hcl_palettes()`
and might need further tweaking in future versions of the package. Thus,
Figures\ \ref{fig:hcl-properties}--\ref{fig:hcl-palettes} as well as
Figures\ \ref{fig:hcl-palettes-principles}--\ref{fig:hcl-palettes-diverging}
all use `swatchplot()` internally. For a simple stand-alone illustration
consider: `swatchplot("Palette" = sequential_hcl(5))`.

>>>>

To provide access to the HCL color palettes from within \pkg{ggplot2} graphics [@color:ggplot2; @color:ggplot2pkg]
suitable discrete, continuous, and binned \pkg{ggplot2} color scales are provided.
The scales are named via the scheme

@@

- `<aesthetic>` is the name of the aesthetic (`fill`, `color`, `colour`).
- `<datatype>` is the type of the variable plotted (`discrete`, `continuous`, `binned`).
- `<colorscale>` sets the type of the color scale used (`qualitative`, `sequential`, `diverging`, `divergingx`).

@@

The function `swatchplot()` is a convenience function for displaying
collections of palettes that can be specified as lists or matrices of
hex color codes. Essentially, it is just a call to the base graphics
`rect()` function but with heuristics for choosing default labels, margins,
spacings, borders, etc. These heuristics are selected to work well for `hcl_palettes()`
and might need further tweaking in future versions of the package. Thus,
Figures\ \ref{fig:hcl-properties}--\ref{fig:hcl-palettes} as well as
Figures\ \ref{fig:hcl-palettes-principles}--\ref{fig:hcl-palettes-diverging}
all use `swatchplot()` internally. For a simple stand-alone illustration
consider: `swatchplot("Palette" = sequential_hcl(5))`.
Optionally, swatches emulating color vision deficiencies (see
Section\ \ref{sec:color_vision_deficiency}) can be added by setting `cvd = TRUE`.
